Article Title

### 2014-01-27 plos.tex
minor

\paragraph{Structure of $C_{\sf sparse+latent}$ estimates}
Estimator $C_{\sf sparse+latent}$ separates two sources of correlations: a network of linear interactions between pairs of neurons and a set of latent units reflecting common fluctuations across the entire population.  These could have multiple physiological causes such as common inputs, cell assembly activation, network fluctuations, or other forms of synchronized activations.

>>>>

\paragraph{Structure of $C_{\sf sparse+latent}$ estimates}
The estimator $C_{\sf sparse+latent}$ separates two sources of correlations: a network of linear interactions between pairs of neurons and a set of latent units reflecting common fluctuations across the entire population.  These could have multiple physiological causes such as common inputs, cell assembly activation, network fluctuations, or other forms of synchronized activations.
